### 2019-04-24 report/chapter03.Rnw
test

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8, fig.height=3.7,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

@@

sig.meta.c <- data.mly %>% select(sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
  gather(key = "meta.analysis.method", value = "sig.meta.analysis") %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))

>>>>

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8.1, fig.height=3.7,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

@@

sig.meta.c <- data.mly %>% select(sig.type, sig.fixef, sig.ranef, sig.ranef.hkn) %>% 
  gather(key = "meta.analysis.method", value = "sig.meta.analysis") %>% mutate(sig.meta.analysis = factor(sig.meta.analysis))
